A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2024-09-26 manuscript/main.tex
Reorganize

Simulated using FakeCairo backend

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/linear_train_vs_test.png}
		\caption{}
		\label{fig:linear_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/quadratic_train_vs_test.png}
		\caption{}
		\label{fig:quadratic_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/sine_train_vs_test.png}
		\caption{}
		\label{fig:sine_train_vs_test}
	\end{subfigure}
	\caption{}
	\label{fig:train_vs_test}
\end{figure}

\section{Results}

\subsection{Classical Testing}

\subsubsection{Function Fitting}
We found that on average the best models for the linear function is KNN (Fig. \siref{fig:linear}),  KRR for quadratic (Fig. \siref{fig:quadratic}), and KNN for sine (Fig. \siref{fig:sine}).

\subsubsection{DDCC}

$t_{ij}^{ab}$

Dimensions reduced using SHapley Additive Explanation (SHAP) values
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/DDCC_feature_set.png}
	\caption{DDCC feature set}
	\label{fig:DDCC_feature_set}
\end{figure}

\subsubsection{BSE}\label{subsubsection:BSE}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/Feat_redR2.png}
	\caption{Feat redR2}
	\label{fig:Feat_redR2}
\end{figure}
% Key: 
% 'ridge': Ridge(),
% 'lasso': Lasso(),
% 'elastic': ElasticNet(),
% 'knn': KNeighborsRegressor(),
% 'rfr': RandomForestRegressor(),
% 'grad': GradientBoostingRegressor(),
% 'svr': SVR(),
% 'krr': KernelRidge(),
% 'gpr': GaussianProcessRegressor()
% \begin{table}[H]
%     \begin{tabular}{||c | c c c||}
%      \hline
%      Training Set Size & Linear & Quadratic  & Sine \\ [0.5ex] 
%      \hline\hline
%      0.1 & SVR & KNN & GPR \\ 
%      \hline
%      0.3 & GPR & KRR & KRR \\
%      \hline
%      0.5 & SVR & KNN & RFR \\
%      \hline
%      0.7& GPR& Grad & RFR \\
%      \hline
%      0.8 & GPR & KRR & SVR \\ [1ex] 
%      \hline
%     \end{tabular}
%     \caption{Function testing}
%     \label{table:function_testing}
% \end{table}

\subsection{5 qubit function fitting}

Fig. \siref{fig:lin5qubits_metric}
Fig. \siref{fig:quad5qubits_metric}
Fig. \siref{fig:sine5qubits_metric}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/5qubit_function_fitting_best.png}
	\caption{REMAKE}
	\label{fig:5qubit_function_fitting_best}
\end{figure}

\subsection{16 qubit function fitting}

Fig. \siref{fig:lin16qubits_metric}
Fig. \siref{fig:quad16qubits_metric}
Fig. \siref{fig:sine16qubits_metric}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_Linear_RUD_AL.png}
	\caption{REMAKE}
	\label{fig:16qubit_Linear_RUD_AL}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_Quadratic_RUD_AL.png}
	\caption{REMAKE}
	\label{fig:16qubit_Quadratic_RUD_AL}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_Sine_RUD_AL.png}
	\caption{REMAKE}
	\label{fig:16qubit_Sine_RUD_AL}
\end{figure}

The best is IQP\textunderscore Full-Pauli-CRX with 5AL and 5 RUD

Missing 0.8 quadratic

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Linear_learning_curve.png}
		\caption{}
		\label{fig:Linear_learning_curve}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Quadratic_learning_curve.png}
		\caption{}
		\label{fig:Quadratic_learning_curve}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Sine_learning_curve.png}
		\caption{}
		\label{fig:Sine_learning_curve}
	\end{subfigure}
	\caption{Baseline denotes IQP\textunderscore Full-Pauli-CRX with 1AL and 1RUD}
	\label{fig:learning_curve}
\end{figure}

\subsection{5 qubit BSE}
Done
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/5qubit_BSE_RUD_AL.png}
	\caption{5qubit BSE RUD AL}
	\label{fig:5qubit_BSE_RUD_AL}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
	\caption{\textcolor{red}{ADD KILL LIST}}
	\label{fig:AllBSE5_circuitdepth_MAE_vs_iterationtime}
\end{figure}

\subsection{16 qubit BSE}

Missing data
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_BSE_RUD_AL.png}
	\caption{16qubit BSE RUD AL}
	\label{fig:16qubit_BSE_RUD_AL}
\end{figure}

\subsection{Error Correction}
TREX/MITIQ ZNE LINEAR/ MITIQ ZNE Richardson

\subsubsection{Function Fitting}
Running
\subsubsection{DDCC}
Not ran yet
\subsubsection{BSE}
Not ran yet

\subsection{IBM Device}

>>>>

Simulated using FakeQuebecbackend

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/linear_train_vs_test.png}
		\caption{}
		\label{fig:linear_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
		\caption{}
		\label{fig:quadratic_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/sine_train_vs_test.png}
		\caption{}
		\label{fig:sine_train_vs_test}
	\end{subfigure}
	\caption{}
	\label{fig:train_vs_test}
\end{figure}

\section{Results}
\subsection{Model Calibration Using Function fitting} 
We used the function fitting to determine if our models were implemented correctly.

\subsubsection{All (5 + 16 qubit)}
Figure \ref{fig:5qubit_Func_funcfit_R2} shows every encoder and ansatz pair explored for the function fitting datasest with 5 qubits.
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Linear_funcfit_R2.png}
		\caption{}
		\label{fig:5qubit_Linear_funcfit_R2}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Quadratic_funcfit_R2.png}
		\caption{}
		\label{fig:5qubit_Quadratic_funcfit_R2}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Sine_funcfit_R2.png}
		\caption{}
		\label{fig:5qubit_Sine_funcfit_R2}
	\end{subfigure}
	\caption{}
	\label{fig:5qubit_Func_funcfit_R2}
\end{figure}

Figure \ref{fig:16qubit_Func_funcfit_R2} shows every encoder and ansatz pair explored for the function fitting datasest with 16 qubits.

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Linear_funcfit_R2.png}
		\caption{}
		\label{fig:16qubit_Linear_funcfit_R2}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Quadratic_funcfit_R2.png}
		\caption{}
		\label{fig:16qubit_Quadratic_funcfit_R2}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Sine_funcfit_R2.png}
		\caption{}
		\label{fig:16qubit_Sine_funcfit_R2}
	\end{subfigure}
	\caption{}
	\label{fig:16qubit_Func_funcfit_R2}
\end{figure}

\subsubsection{RUD + AL (5 + 16 qubit)}\label{subsection:func_depth}
The best, median, and worst 5 were chosen from the 16 qubit data.

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Linear_RUD_AL.png}
		\caption{}
		\label{fig:16qubit_Linear_RUD_AL}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Quadratic_RUD_AL.png}
		\caption{}
		\label{fig:16qubit_Quadratic_RUD_AL}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Sine_RUD_AL.png}
		\caption{}
		\label{fig:16qubit_Sine_RUD_AL}
	\end{subfigure}
	\caption{}
	\label{fig:16qubit_Func_RUD_AL}
\end{figure}

\subsubsection{Learning curve}
The best models from Section \ref{subsection:func_depth} were then used to compare them with classical machine learning models using learning curves, where the test set was held to 10 points, while the training data was varied from 10-80 points.

For the linear model with 16 qubits, the IQP encoding with the Full Pauli CRZ ansatz layer outperforms the classical models at 10\% of the training data, as show in  Fig. \ref{fig:linear_learning_curves}.
The quantum model is less overfit and has a more accurate test score than any of the classical models. 
As the training set size increases, the quantum model maintains an average train and test R$^{2}$ of 0.98, while the classical models maintain an average train and test R$^{2}$ of 0.99.
\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/Function_Fitting/linear_learning_curves.png}
	\caption{Linear learning curve}
	\label{fig:linear_learning_curves}
\end{figure}

\subsubsection{Error mitigation}
FakeQuebec backend
ZNE linear and Richardson
TREX
Without

\subsubsection{Real device}
IBM Quebec!

\subsection{BSE}

\subsubsection{Classical testing}
After an extensive search of the possible moleuclar representations for the BSE dataset, we decided to use Morgan fingerprints.
To map this set of features down to 5 and 16 qubits, we analyzed using SHapley Additive exPlanation (SHAP) values and principal component analysis.
Based of of the analysis from Fig. \ref{fig:Feat_redR2}, we chose to use the set of features reduced using PCA due to the more accurate, albiet overfit data.
\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/BSE/Feat_redR2.png}
	\caption{BSE Feature Reduction}
	\label{fig:Feat_redR2}
\end{figure}
\subsubsection{All (5 + 16 qubit)}
Using the aforementioned datasets, along with the 168 encoder-ansatz pairs we analyzed the cost of modeling the BSE dataset using the 5 qubit feature set first.

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/BSE/5qubit_BSE_MAE.png}
	\caption{5 qubit BSE MAE (kcal/mol)}
	\label{fig:5qubit_BSE_MAE}
\end{figure}

Using this data, we analyzed the mean time per training iteration versus the MAE and circuit depth. 
We found that within the 168 encoder-ansatz pairs, there existed a bimodal distribution, where there were a set of 70 circuits with the mean time per iteration greater than 100 seconds and those with less.
Going forward, we will only use the set of circuits that belong to the set with mean iteration times less than 100 seconds due to cost considerations.
\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/BSE/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
	\caption{5 qubit BSE MAE (kcal/mol)}
	\label{fig:AllBSE5_circuitdepth_MAE_vs_iterationtime}
\end{figure}

For the 70 circuits that belong to those with iterations less than 100 seconds for the BSE 5 qubit set, we used these for the 16 qubit as well and found that...

\subsubsection{RUD + AL (5 + 16 qubit)}
Based off of the improvements shown in the function fitting dataset, we only used the best encoding ansatz pair for the real datasets
For the 5 qubit, it is A2 HWE-CNOT

\subsubsection{Error mitigation}
\subsubsection{Real device}

\subsection{DDCC}

\subsubsection{Classical testing}
\subsubsection{All (5 + 16 qubit)}
\subsubsection{RUD + AL (5 + 16 qubit)}
\subsubsection{Error mitigation}
\subsubsection{Real device}

\section{Conclusion}

Molecular representations specifically for QML
Distributed QC to incorporate more features
